DraftFunctions

### 2021-12-03 R/DraftFunctions.Rmd
ONF modifications

```{r SpeciesCriteria table code}
SpeciesCriteria <- read_csv("D:/VSC Kourou/DATA/SpeciesCriteria.csv",
                            col_types = cols(Commercial = col_factor(levels = c("0",
                                                                                "1", "2")), MinFD = col_number(),
                                             UpMinFD = col_number(), MaxFD = col_number()),
                            locale = locale(encoding = "Latin1")) %>%
  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T)
# unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)

@@

usethis::use_data(SpeciesCriteria)
```

>>>>

```{r SpeciesCriteria table code}
SpeciesCriteria <- read_csv("D:/VSC Kourou/DATA/SpeciesCriteria.csv",
                            col_types = cols(Commercial = col_factor(levels = c("0",
                                                                                "1", "2")), MinFD = col_number(),
                                             UpMinFD = col_number(), MaxFD = col_number()),
                            locale = locale(encoding = "Latin1")) %>%
  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) %>% 
  mutate(Aggregative = ifelse(VernName == "Angélique" | VernName == "Gonfolo rose",
                              TRUE, FALSE))
# unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)

@@

# usethis::use_data(SpeciesCriteria, overwrite = TRUE)
```
```{r}
ScenariosTable <- read_csv("D:/VSC Kourou/DATA/ScenariosTable.csv", 
    col_types = cols(Winching = col_factor(levels = c("0", 
        "1", "2")), DirectionalFelling = col_factor(levels = c("0", 
        "1", "2"))), trim_ws = TRUE)

# usethis::use_data(ScenariosTable,overwrite = TRUE)
```
